\cvsection{Employment}

\begin{cventry}
    {Google}
    {Software Engineer}
    {Mar. 2020 to Present}
    {Java, JavaScript, HTML, CSS, Closure Template}{}
    \begin{cvitems}
        \item Working on the Google Docs Collaboration team as a full stack software engineer.
        \item Implementing novel features for Google Docs, Sheets, and Slides that enable seamless collaboration between users.
    \end{cvitems}
\end{cventry}

\begin{cventry}
    {Mercer Street Friends}
    {Full Stack Web Developer}
    {Aug. to Dec. 2019}
    {Ruby, PostgreSQL, HTML, SCSS}{Rails, SendGrid}
    \begin{cvitems}
        \item Implemented an MVC full stack web application with \textsl{Ruby on Rails} and \textsl{PostgreSQL} for the Trenton-based non-profit organization, Mercer Street Friends, to effectively manage its internal work order requests.
        \item Applied the principles of responsive web design to provide a pleasant user experience on desktop, tablet, and mobile devices.
    \end{cvitems}
\end{cventry}

\begin{cventry}
    {Google}
    {Software Engineer}
    {May to Aug. 2019}
    {Java, JavaScript, HTML, CSS, Closure Templates}{}
    \begin{cvitems}
        \item Interned on the Google Sites team to develop a feedback feature for ensuring sites remain current.
        \item Built a fully asynchronous backend with \textsl{Java} and a modular frontend with a component-based \textsl{JavaScript} framework.
        \item Internationalized the existing email infrastructure by implementing proper text alignment for right-to-left languages. 
    \end{cvitems}
\end{cventry}

\begin{comment}
    \begin{cventry}
        {The College of New Jersey (TCNJ)}
        {Computer Science Department Tutor}
        {Apr. 2018 to May 2019}
        {Java, C++, C, Ruby, PostgreSQL, Regular Expressions}{Rails}
        \begin{cvitems}
            \item Tutoring TCNJ students in computer science coursework concerning topics such as object-oriented programming, data structures, discrete math, algorithms, computer architecture, operating systems, databases, and software engineering.
        \end{cvitems}
    \end{cventry}
\end{comment}

\begin{comment}
    \begin{cventry}
        {Mercer Street Friends}
        {Full Stack Web Developer}
        {Jan. to Feb. 2019}
        {Ruby, PostgreSQL, HTML, SCSS}{Rails, SendGrid}
        \begin{cvitems}
            \item Implemented a novel MVC full stack web application with \textsl{Ruby on Rails} and \textsl{PostgreSQL} for the Trenton-based non-profit organization, Mercer Street Friends, to effectively publicize the positive impacts of its charitable work.
            \item Applied the principles of responsive web design to provide a pleasant user experience on desktop, tablet, and mobile devices.
        \end{cvitems}
    \end{cventry}
\end{comment}

\begin{comment}
    \begin{cventry}
        {Varsity Tutors}
        {Java Tutor}
        {Sept. 2017 to May 2018}{}{}
        \begin{cvitems}
            \item Tutored AP Computer Science students regularly in an online one-on-one setting.
        \end{cvitems}
    \end{cventry}
\end{comment}

\begin{cventry}
    {The College of New Jersey (TCNJ)}
    {Mentored Undergraduate Student Experience (MUSE) Researcher}
    {June to July 2017}
    {Java, Python}{Weka, SVM\textsuperscript{Light}, LIBSVM, scikit-learn, SLURM}
    \begin{cvitems}
        \item Collaborated with a student in a selective 8-week full-time undergraduate research program.
        \item Developed an automated machine learning curve analysis infrastructure in \textsl{Java} with support for pluggable classifiers.
        \item Implemented active learning stopping methods to train text classifiers with minimal training data in \textsl{Python}.
    \end{cvitems}  
\end{cventry}

\begin{comment}
    \begin{cventry}
        {The College of New Jersey (TCNJ)}
        {Undergraduate Student Researcher}
        {Jan. to May 2017}
        {Java, Python}{Weka, scikit-learn, SLURM}
        \begin{cvitems}
            \item Collaborated with a team of 5 to test machine learning algorithms with varying amounts of training data.
            \item Developed a text normalization and feature extraction algorithm for text classification using stop words and term frequency-inverse document frequency.
        \end{cvitems}
    \end{cventry}
\end{comment}
