\cvsection{Projects}

\begin{cventry}
    {\href{https://jillmarbach.com}{Jill Marbach's Portfolio Website and Blog}}{}
    {Feb. to Apr. 2020}
    {JavaScript, HTML, Markdown, CSS}{Gatsby, React, Styled Components, Netlify CMS}
    \begin{cvitems}
        \item Implemented a portfolio website and blog, complete with a CMS and search, for a student at The College of New Jersey.
        \item Incorporated responsive typography and intrinsic web design to create a website with a dynamic feel.
    \end{cvitems}
\end{cventry}

\begin{comment}
    \begin{cventry}
        {The Dandy Programming Language}{}
        {April 2019 to Present}
        {Kotlin}{ANTLR}
        \begin{cvitems}
            \item Designing and programming a compiler for a novel multi-paradigm functional/imperative programming language with parametric polymorphism, higher kinded types, and comprehensive type inference.
        \end{cvitems}
    \end{cventry}
\end{comment}

\begin{comment}
    \begin{cventry}
        {Spotify Web API Wrapper and Object-Relational Mapping}{}
        {Jan. 2019 to Present}
        {TypeScript}{Rollup.js, Babel}
        \begin{cvitems}
            \item Developing an isomorphic Spotify Web API wrapper in \textsl{TypeScript} with an object-oriented abstraction layer.
            \item Implementing automatic paging, OAuth token refreshing, and rate-limit timeouts.
        \end{cvitems}  
    \end{cventry}    
\end{comment}

\begin{comment}
    \begin{cventry}
        {Functional Linear Algebra Library}{}
        {Aug. to Dec. 2018}
        {Kotlin}{Gradle}
        \begin{cvitems}
            \item Implemented a functional linear algebra library with lazy evaluation and function composition.
            \item Inspired by the Kotlin Sequence interface.
        \end{cvitems}  
    \end{cventry}
\end{comment}

\begin{comment}
    \begin{cventry}
        {\href{https://github.com/TomerAberbach/tomeraberbach.github.io}{Tomer Aberbach Static Website Generator}}{}
        {May to July 2018}
        {JavaScript, HTML, Markdown, Handlebars, CSS, SVG, YAML}{Node.js, Gulp.js}
        \begin{cvitems}
            \item Designed and developed a static website generator for my portfolio website.
            \item Automated pagination and optimized assets using transpilation and minification.
        \end{cvitems}  
    \end{cventry}
\end{comment}

\begin{comment}
    \begin{cventry}
        {\href{https://wtsr.tomeraberba.ch}{WTSR 91.3FM Web Player}}{}
        {Feb. 2018}
        {JavaScript, HTML, CSS}{Firebase, Node.js, Gulp.js, ACRCloud}
        \begin{cvitems}
            \item Designed and programmed an online web player for TCNJ's official fully student-run radio station with a \textsl{Node.js} backend.
            \item Incorporated audio controls, audio fingerprinting for real-time song identification, and Spotify song links.
            \item Won ``Best Technical Project'' at the HackTCNJ hackathon.
        \end{cvitems}
    \end{cventry}
\end{comment}

\begin{cventry}
    {\href{https://github.com/TomerAberbach/mano-simulator}{Mano Basic Computer Assembler and Simulator}}{}
    {Oct. 2017 to Jan. 2018}
    {Java}{JavaFX}
    \begin{cvitems}
        \item Developed, tested, and deployed an assembler and hardware simulator for the Mano Basic Computer, a 16-bit computer, complete with a user interface and documentation using \textsl{JavaFX}.
        \item Was adopted for regular academic use in a college-level computer architecture course.
    \end{cvitems}
\end{cventry}
